---
title: "How Americans View Biden's Response To The Coronavirus Crisis"
author: "Cliff Lee"
date: "8/26/2021"
output: html_document
---

## Introduction

The article shows various graphs comparing how Americans view Biden's handling of the pandemic to that of Trump. Americans answered questions regarding the following subjects: Presidential response; their feelings about infections; and feelings about the economy.

This assignment focuses on data concerning the following question: __*Do Americans approve of Biden's response to the coronavirus crisis?*__


__Article Link:__ https://projects.fivethirtyeight.com/coronavirus-polls/


## Initialization and package inclusion

The first block sets this project's configurations and include packages for the rest of the markdown file.
```{r setup}
knitr::opts_chunk$set(echo = TRUE)

# Packages listings

# For str_replace function
library(stringr)

# Basic data frame operations
library(tidyverse)

```


## Load CSV into a data_frame variable
```{r}

# Load the CSV from Github
data_frame = read.table(file="https://raw.githubusercontent.com/cliftonleesps/607_acq_mgt/main/covid-19-polls-master/covid_approval_polls_adjusted.csv", header=TRUE,sep=",")

```


## Subsetting

This block performs a couple of basic data frame operations:

* Filters out observations
* Removes unnecessary columns
* Reorders columns

```{r}
# Since we only want to know about Biden's approval rating, we'll filter out observations where he is not the President
data_frame <- filter(data_frame, subject == 'Biden')

# Remove a few unnecessary columns
data_frame <- select(data_frame, party,enddate, pollster, samplesize,approve_adjusted,disapprove_adjusted)

# Sort by Poll Date, party
data_frame <- arrange(data_frame, enddate, party)

# Reorder the columns
data_frame <- data_frame[,c("enddate","pollster","samplesize","party","approve_adjusted","disapprove_adjusted")]

```




## Transformations

The next block further helps the reader by renaming observations to more meaningful values. Any explanation of values can be retrieved via their Github page listed below.

__Link:__ https://github.com/fivethirtyeight/covid-19-polls


```{r}


# Map party key value pairs
data_frame$party <- str_replace(string=data_frame$party, pattern="^D$", replacement="Democrat")
data_frame$party <- str_replace(string=data_frame$party, pattern="^R$", replacement="Republican")
data_frame$party <- str_replace(string=data_frame$party, pattern="^I$", replacement="Independent")
data_frame$party <- str_replace(string=data_frame$party, pattern="^all$", replacement="All")

# Transform participants by rounding them to integers
data_frame$samplesize <- round(data_frame$samplesize)

# Round the adjusted approval/disapproval percentage columns to 1 significant digit
data_frame$approve_adjusted <- round(data_frame$approve_adjusted, digits = 1)
data_frame$disapprove_adjusted <- round(data_frame$disapprove_adjusted, digits = 1)


# Rename headers for readability
data_frame <- rename(data_frame, Party = party)
data_frame <- rename(data_frame, Participants = samplesize )
data_frame <- rename(data_frame, Pollster = pollster )
data_frame <- rename(data_frame, "Approval Pct" = approve_adjusted)
data_frame <- rename(data_frame, "Disapproval Pct" = disapprove_adjusted)
data_frame <- rename(data_frame, "Poll Date"= enddate)


# Show the final subset
head(data_frame, n=10)
```


# Conclusions

The answer to the central question is yes, a majority of Americans approve of Biden's handling of the corona virus epidemic. His latest poll numbers among independents remains 57%, 25% for Republicans and 92% for Democrats.  


