---
title: "SQL & R"
author: "Cliff Lee"
date: "8/31/2021"
output:
  html_document: default
  pdf_document: default
---

### Brief
This file accomplishes a few tasks:
* Reads a CSV of movie ratings from GitHub
* Separates the CSV values into three tibbles
* Creates three tables from the tibble variables
* Performs basic queries from the tables

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Tibble operations
library(tidyverse)

# For data cleanup
library(stringr)

# Creating tables
library(dbplyr)

# Connection to a DB
library(DBI)

```

### Read the CSV of survey results
```{r}
# Get the data from Github and specify the string "Did not see" as a NA value
# This helps with creating the tables later
raw_review <- read_csv("https://raw.githubusercontent.com/cliftonleesps/607_acq_mgt/main/week2/rate_recent_movies.csv", show_col_types=FALSE, na=c("Did not see"))

```

### Database connection and importing
```{r}
# Connect to the database using the password from an environment variable
db_connection <- dbConnect(RMariaDB::MariaDB(), user = "rstudio", password = Sys.getenv("RSTUDIO_PASS"), dbname = 'movie_reviews')


# Make a list for creating the review connector table
viewer_names <- raw_review$`Your name`

```


### Create the viewer table
```{r}

# The viewer table has three columns:
# PK: viewer_id 
#     viewer_name
#     entry - when the response was submitted to Google Form
viewer <- tibble::tibble(
  viewer_id = 1:length(raw_review$`Your name`),
  viewer_name = raw_review$`Your name`,
  entry = raw_review$Timestamp
)
copy_to(db_connection, viewer, overwrite = TRUE, temporary = FALSE)

```


### Create the movie title table
```{r}
titles <- colnames(raw_review)
titles <- titles[-c(1,2)] 

movie <- tibble::tibble(
  movie_id = 1:length(titles),
  title = titles,
)
copy_to(db_connection, movie, overwrite = TRUE, temporary = FALSE)

```

### Create a connector table

```{r}
# initialize the review model
raw_review <- select(raw_review, all_of(titles))
review <- tibble::tibble(
  movie_id = rep(1, length(viewer_names)),
  viewer_id = 1:length(viewer_names),
  rating = str_replace(raw_review[[1]], pattern = " Stars$", replacement = "")
)

# remove the first column
titles <- titles[-c(1)] 
raw_review <- select(raw_review, all_of(titles))

# iterate through the rest of the raw_review
for(i in seq_along(raw_review)) {       
  review <- review %>% add_row(
    movie_id = rep(i+1, length(viewer_names)),
    viewer_id = 1:length(viewer_names),
    rating = str_replace(raw_review[[i]], pattern = " Stars$", replacement = "")
  )
}

copy_to(db_connection, review, overwrite=TRUE, temporary = FALSE)

```


### Sample Query #1

Example query: Return movie titles ordered by the number of reviews

```{r}

# Use dplyer to query and join the movie and review tables

# Natural join the review and movie tables
movies <- as_tibble(review)
number_of_views <- movies %>%
  select (rating, movie_id) %>%
  inner_join(movie) %>%
  filter( !is.na(rating) ) %>%
  count(movie_id)

# Join again for the titles
movie_titles <- number_of_views %>%
  inner_join(movie)
movie_titles <- arrange(movie_titles, desc(n) )

# Clean up for displaying
movie_titles <- select (movie_titles, c("n", "title"))
movie_titles <- rename(movie_titles, "Number of Viewings" = n,"Title" = title)


movie_titles
```



### Sample Query #2

Example query: Return the median rating for all movies

```{r}
median_movie_ratings <- movies %>%
  select (rating, movie_id) %>%
  inner_join(movie) 

median_movie_ratings <- median_movie_ratings %>%
  group_by(movie_id, title) %>%
  summarize(median_rating = median(as.numeric(rating), na.rm = TRUE)) 

median_movie_ratings <- arrange( median_movie_ratings, desc(median_rating))

median_movie_ratings
```


```{r}
# Close the db connection so we don't tie up a server connection
dbDisconnect(db_connection)
```