---
title: "Week3 - Character Manipulation and Date Processing"
author: "Cliff Lee and Victoria McEleney"
date: "9/7/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


# Tibble operations
library(tidyverse)

# For data cleanup
library(stringr)

library(htmlwidgets)

```


#### 1. Provide code that identifies the majors that contain either “DATA” or “STATISTICS”

Using the 173 majors listed in fivethirtyeight.com’s College Majors dataset [https://fivethirtyeight.com/features/the-economic-guide-to-picking-a-college-major/], provide code that identifies the majors that contain either "DATA" or "STATISTICS"

```{r}

# Load the CSV from Github
all_ages = read_csv("https://raw.githubusercontent.com/cliftonleesps/607_acq_mgt/main/week3/college-majors/all-ages.csv", show_col_types=FALSE)

# Now grep for DATA or STATISTICS
data_statistics_majors <- grep(pattern = "(STATISTICS|DATA)", all_ages$Major)

# Output the matched majors
for (i in (data_statistics_majors)) {
  cat (sprintf("%s\n", all_ages$Major[i]))
}
```


### 2. Write code that transforms the data below:

[1] "bell pepper"  "bilberry"     "blackberry"   "blood orange"
[5] "blueberry"    "cantaloupe"   "chili pepper" "cloudberry"  
[9] "elderberry"   "lime"         "lychee"       "mulberry"    
[13] "olive"        "salal berry"

Into a format like this:

c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

```{r}
# Create a character vector representing the original comma separted, data string
stuff <- paste("bell pepper, bilberry, blackberry, blood orange, blueberry, cantaloupe, chili pepper, cloudberry, elderberry, lime, lychee, mulberry, olive, salal berry")

# Initialize
output <- ""

# Concatenate each element wrapped in double quotes and a comma
for (i in (str_split(stuff, " *, *"))) {
  output <- str_c(output, '"',i,'"', sep="", collapse=",")
}

# Wrap with parentheses
output <-str_c('c(',output,')', sep="", collapse="")

# Display the result
cat(output)

```


The two exercises below are taken from R for Data Science, 14.3.5.1 in the on-line version:

#### 3. Describe, in words, what these expressions will match:


##### (.)\\1\\1 

will match any 3 consecutive characters (ex: CCC)


##### "(.)(.)\\2\\1" 

will match any 2 characters followed by the same 2 captured characters in reverse order (ex: eppe)


##### (..)\1 

will match any 2 characters followed by the same 2 characters (ex: anan)


##### "(.).\\1.\\1" 

will match any character followed by any character, followed by the 1st captured character, followed by any character apart from 1st captured character, followed by the 1st captured character (ex: anana, anama)


##### "(.)(.)(.).*\\3\\2\\1" 

will match any 3 characters, followed by any or no characters, followed by the first captured 3 characters in reverse order (ex: aprrpa, apricotrpa)



#### 4. Construct regular expressions to match words that:

##### Start and end with the same character.


```{r}
words <- c("sflfs", "tldkf", "jh5jlsadj", "bnmasd")
words[str_detect(words, "^(.)((.*\\1$)|\\1?$)")]
```



##### Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)


```{r}
words <- c("ChurCh", "banana", "inning", "falefal", "jukebox", "killjoy" )
str_view(words, "([a-zA-Z][a-zA-Z]).*\\1", match = TRUE)
```


##### Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)


```{r}
words <- c("inning", "mannning", "Outbound", "LOLLIPOP")
str_view(words, "([a-zA-Z]).*\\1.*\\1", match = TRUE)

```

